Bayesian exponential random graph modeling of KWL Burial network

### 2020-11-04 analysis/paper/paper.Rmd
adjust the parameter for ritual

<!--burial study- network analysis-->
Burial analysis has long developed in archaeology to study societies through mortuary practices, such as cultural and biological records in burial contexts, reflecting the social status or identity of the deceased [@Binford1971; @Saxe1970]. Despite the criticism for not considering the burial manipulation by the living or situations of less connection to real life [@Hodder1980; @Pearson1982], burial analysis with a quantitative approach is still effective to answer questions related to social representations with both archaeological contexts of death and life in mind [@Chapman2003]. Mortuary practices include burial forms, grave goods, and related ritual practices that structure the material configuration of burials can represent social relations between members of a community, allowing the inference for social structures [@Byrd1995; @Seikel2011]. The development of network science and graph theory provides many new tools for the study of the relations between burials and exploration of their social implications [@Sosna2013]. This means we can use data from burials to study social differences to answer questions related to social inequality and complexity [@Ehrhardt2009; @Gamble2002; @Janes2013; @Johansen2015]. For example, burial goods can reflect social practices in broader cultural contexts to represent personal wealth, social roles, or traditional customs. Burials with the same mortuary practices may indicate some similar underlying social relations, for example, individuals with grave goods in common that share similar access to trade, exchange, and gifting networks [eg. @Coward2013, pp. 252]. Identifying the structure of relationships among burials can give insights into the structure of social organization.

>>>>

<!--burial study- network analysis-->
Burials analysis has long developed in archaeology as an approach to study past social structure through mortuary practices, such as cultural and biological records in burial contexts, that can represent social status or identity of the deceased [@Binford1971; @Saxe1970]. Despite the criticism for overlooking the burial manipulation by the living that does not necessarily connect to the real life [@Hodder1980; @Pearson1982], with comparisons between different archaeological contexts of death and life in mind, burials can still provide valuable information to infer past societies [@Chapman2003]. For example, mortuary practices, including burial forms, grave goods, and ritual behaviors, that structure the material configuration of burials can represent social relations between members of a community, allowing the inference for social structures [@Byrd1995; @Seikel2011]. To study social relations, the recent development of network science and graph theory provides many new tools for the exploration and analyzing the structure of relational data [@Brandes2013]. This means we can answer anthropological questions about social differentiation, and social inequality or complexity based on our assumptions of archaeological data [@Ehrhardt2009; @Gamble2002; @Janes2013; @Johansen2015]. For example, burial goods can reflect social practices in broader cultural contexts to represent personal wealth, social roles, or traditional customs. The flow of material goods  Burials with the same goods may indicate some similar underlying social relations where individuals share similar access to trade, exchange, and gifting networks [eg. @Coward2013, pp. 252]. Identifying the structure of relationships among burials can give insights into the structure of social organization.
